HPC--101\\Onboarding

### 2016-07-29 hpc_101/paper.tex
fixed typo on globus endpoint and swtiched from tmi to shm:tmi

\begin{frame}
	\frametitle{Globus}\footnotesize
\begin{block}{How do I get Globus?}
To utilize Globus, follow the following steps:
\begin{itemize}\tiny
\item Register for a Globus Online account -- \url{https://www.globusonline.org/signup}
\item Sign in to Globus Online (using your Globus Online username and password) -- \url{https://www.globusonline.org/signin}
\item Select ‘Start Transfer’ under ‘File Transfer’, or from the drop down menu in the top bar
\item You can view the list of available endpoints by clicking the button on the ‘Endpoint’ drop down box
\begin{itemize}\tiny
 \item Each of the login nodes is also an endpoint: \textbf{\emph{UHHPC1}} \& \textbf{\emph{UHHPC2}}
\end{itemize}
\item Once you select an endpoint, a login window will pop up. You can access the UHHPC endpoints by simply using your UH username and password. Enter your UH accounts username in the ‘Username’ field and UH accounts password in the ‘Password’ field and click ‘Authenticate’. 
\item You will see a listing of the contents of your home directory on the UH HPC. Double click on a directory to view its contents
\item Select a file or directory and click on the highlighted ‘arrow button’ to initiate the transfer
\end{itemize}
\end{block}
~\\
These instructions can also be found on the {\ci} website:~\\
{\footnotesize \href{http://www.hawaii.edu/its/ci/hpc-resources/hpc-tutorials/globus-quick-start-guide/}{http://www.hawaii.edu/its/ci/hpc-resources/hpc-tutorials/globus-quick-start-guide/}}
\end{frame}

@@

@@

\#!/bin/bash
\#SBATCH \ddash{}job-name=GPU\_example
\textcolor{blue}{\#SBATCH \ddash{}partition=gpu.q}
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\textcolor{blue}{\#SBATCH \ddash{}cpus-per-task=10}
\textcolor{blue}{\#SBATCH \ddash{}mem=11000} \#\# max amount of memory per node you require
\textcolor{blue}{\#SBATCH \ddash{}gres=gpu:NV-K40:2 } \#\# request both GPUs in the GPU node.
\#\#\# To request only 1 of the two GPUs in the node, you would do: gpu:NV-K40:1
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\#!/bin/bash
\#SBATCH \ddash{}job-name=MPI\_example
\textcolor{blue}{\#SBATCH \ddash{}partition=exclusive.q}
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\textcolor{blue}{\#SBATCH \ddash{}nodes=4}
\textcolor{blue}{\#SBATCH \ddash{}tasks-per-node=20}
\textcolor{blue}{\#SBATCH \ddash{}cpus-per-task=1}
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\#\# All options and environment variables found on schedMD site: \href{http://slurm.schedmd.com/sbatch.html}{http://slurm.schedmd.com/sbatch.html}
\#\# Intel MPI manual: \href{https://software.intel.com/en-us/mpi-refman-lin-html}{https://software.intel.com/en-us/mpi-refman-lin-html}
export OMP\_NUM\_THREADS=\$\{SLURM\_CPUS\_PER\_TASK\}
export I\_MPI\_FABRICS=tmi  
export I\_MPI\_PMI\_LIBRARY=/opt/local/slurm/default/lib64/libpmi.so

@@

\begin{frame}	
\frametitle{FAQ}
\begin{itemize}
  \item Can I run a display program on the cluster?
    \begin{itemize}
      \item \textbf{Answer:} Yes, but not from the login nodes.  To follow cluster usage policies, please run X11 applications from a compute node.  Please see the following steps.
\end{itemize}
\end{itemize}
 \begin{block}{Interactive session with X11}\tiny  
       \begin{enumerate}
      \item Connect via SSH using the -Y option, X11 forwarding enabled
      \item run srun.x11 to start a session on a node
      \end{enumerate}
      \
      ~\\
      ~\\
      $[$local \ctilde$]$\$ ssh -Y user99@uhhpc1.its.hawaii.edu	~\\
      $[$login \ctilde$]$\$ srun.x11 \ddash{}immediate \ddash{}partition sb.q \ddash{}nodes 1 \ddash{}cpus-per-task 1 \ddash{}tasks-per-node 1 \ddash{}time 0-01:00:00	~\\
      $[$compute-0001 \ctilde$]$\$ xterm	~\\
 \end{block}

>>>>

\begin{frame}
	\frametitle{Globus}\footnotesize
\begin{block}{How do I get Globus?}
To utilize Globus, follow the following steps:
\begin{itemize}\tiny
\item Register for a Globus Online account -- \url{https://www.globusonline.org/signup}
\item Sign in to Globus Online (using your Globus Online username and password) -- \url{https://www.globusonline.org/signin}
\item Select ‘Start Transfer’ under ‘File Transfer’, or from the drop down menu in the top bar
\item You can view the list of available endpoints by clicking the button on the ‘Endpoint’ drop down box
\begin{itemize}\tiny
 \item Each of the login nodes is also an endpoint: \textbf{\emph{UH-HPC1}} \& \textbf{\emph{UH-HPC2}}
\end{itemize}
\item Once you select an endpoint, a login window will pop up. You can access the UHHPC endpoints by simply using your UH username and password. Enter your UH accounts username in the ‘Username’ field and UH accounts password in the ‘Password’ field and click ‘Authenticate’. 
\item You will see a listing of the contents of your home directory on the UH HPC. Double click on a directory to view its contents
\item Select a file or directory and click on the highlighted ‘arrow button’ to initiate the transfer
\end{itemize}
\end{block}
~\\
These instructions can also be found on the {\ci} website:~\\
{\footnotesize \href{http://www.hawaii.edu/its/ci/hpc-resources/hpc-tutorials/globus-quick-start-guide/}{http://www.hawaii.edu/its/ci/hpc-resources/hpc-tutorials/globus-quick-start-guide/}}
\end{frame}

@@

	\end{block}
\btVFill
\begin{center}Interactive sessions terminate when the specified time has elapsed~\\or if you give the \textbf{exit} command \end{center}

@@

\#!/bin/bash
\#SBATCH \ddash{}job-name=GPU\_example
\textcolor{blue}{\#SBATCH \ddash{}partition=gpu.q}
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\textcolor{blue}{\#SBATCH \ddash{}cpus-per-task=10}
\textcolor{blue}{\#SBATCH \ddash{}mem=11000} \#\# max amount of memory per node you require
\textcolor{blue}{\#SBATCH \ddash{}gres=gpu:NV-K40:2 } \#\# request both GPUs in the GPU node
\#\#\# To request only 1 of the two GPUs in the node, you would do: gpu:NV-K40:1
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\#!/bin/bash
\#SBATCH \ddash{}job-name=MPI\_example
\textcolor{blue}{\#SBATCH \ddash{}partition=exclusive.q}
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\textcolor{blue}{\#SBATCH \ddash{}nodes=4}
\textcolor{blue}{\#SBATCH \ddash{}tasks-per-node=20}
\textcolor{blue}{\#SBATCH \ddash{}cpus-per-task=1}
\textcolor{blue}{\#\#SBATCH \ddash{}mem=11000} \# Memory should not be set for jobs in exclusive.q
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\#\# All options and environment variables found on schedMD site: \href{http://slurm.schedmd.com/sbatch.html}{http://slurm.schedmd.com/sbatch.html}
\#\# Intel MPI manual: \href{https://software.intel.com/en-us/mpi-refman-lin-html}{https://software.intel.com/en-us/mpi-refman-lin-html}
export OMP\_NUM\_THREADS=\$\{SLURM\_CPUS\_PER\_TASK\}
export I\_MPI\_FABRICS=shm:tmi  
export I\_MPI\_PMI\_LIBRARY=/opt/local/slurm/default/lib64/libpmi.so

@@

\begin{frame}	
\frametitle{FAQ}
\begin{itemize}
  \item Can I run a display program on the cluster?
    \begin{itemize}
      \item \textbf{Answer:} Yes, but not from the login nodes.  To follow cluster usage policies, please run X11 applications from a compute node.  Please see the following steps.
\end{itemize}
\end{itemize}
 \begin{block}{Interactive session with X11}\tiny  
       \begin{enumerate}
      \item Connect via SSH using the -Y option, X11 forwarding enabled
      \item run srun.x11 to start a session on a node
      \end{enumerate}
      \
      ~\\
      ~\\
      $[$local \ctilde$]$\$ ssh -Y user99@uhhpc1.its.hawaii.edu	~\\
      $[$login \ctilde$]$\$ srun.x11 \ddash{}partition sb.q \ddash{}nodes 1 \ddash{}cpus-per-task 1 \ddash{}tasks-per-node 1 \ddash{}time 0-01:00:00	~\\
      $[$compute-0001 \ctilde$]$\$ xterm	~\\
 \end{block}
